Expectations bias moral evaluations

### 2018-06-04 paper/paper.Rmd
made draft figures readable

```{r make figures, include=FALSE}
# plt <- plot(marginal_effects(fit_exp1))
```

@@

plot(marginal_effects(fit_exp1, "trial"))
```

@@

```{r figure2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Marginal expected response (1-5 scale) in Experiment 2. A response of 3 indicates indifference, a response below 3 indicates a bias to choose the less likely response as more upsetting. (DRAFT FIGURE)"}

plot(marginal_effects(fit_exp2, "trial"))
```

>>>>

```{r make figures, include=FALSE}
fig1 <- plot(marginal_effects(fit_exp1, "trial"))
fig2 <- plot(marginal_effects(fit_exp2, "trial"))
```

@@

fig1$trial +
  coord_cartesian(ylim=c(0,1)) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

@@

```{r figure2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Marginal expected response (1-5 scale) in Experiment 2. A response of 3 indicates indifference, a response below 3 indicates a bias to choose the less likely response as more upsetting. (DRAFT FIGURE)"}
fig2$trial +
  coord_cartesian(ylim=c(2.25,3.25)) +
  geom_hline(yintercept = 3, linetype = "dashed") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
